---
title: "Assignment 5, Part 1"
author: "Chenyang Wu"
date: "2022/2/16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Info
#### **GitHub user name**: Wuris
#### **Date**: 2022/2/16
#### **GitHub Link**: https://github.com/Wuris/Rentrez.git

### Import the Sequences.csv file.
```{r}
setwd("E:/Underguaduate/4th Fourth year/BIOL 432/Week 6/Assignment 5 - Sequence Data Assignment/Rentrez")
A5Data <- read.csv("Sequences.csv")
```

### Count the number of each base pair (A, T, C and G), in each of the three sequences.

```{r}
# Separate each base pair for each sequence.
seq1 <- strsplit(A5Data$Sequence, "")[[1]]
seq2 <- strsplit(A5Data$Sequence, "")[[2]]
seq3 <- strsplit(A5Data$Sequence, "")[[3]]

# Calculate the total number of base pair.
tot1 <- sum(nchar(seq1))
tot2 <- sum(nchar(seq2))
tot3 <- sum(nchar(seq3))
```

```{r}
# Create the for loop to calculate the number of each base pair for each sequence.
a1 = a2 = a3 = 0
t1 = t2 = t3 = 0
c1 = c2 = c3 = 0
g1 = g2 = g3 = 0

for(i in seq1){
    if(i == "A"){a1 <- a1 + 1}
    if(i == "T"){t1 <- t1 + 1}
    if(i == "C"){c1 <- c1 + 1}
    if(i == "G"){g1 <- g1 + 1}
}

for(i in seq2){
    if(i == "A"){a2 <- a2 + 1}
    if(i == "T"){t2 <- t2 + 1}
    if(i == "C"){c2 <- c2 + 1}
    if(i == "G"){g2 <- g2 + 1}
}

for(i in seq3){
    if(i == "A"){a3 <- a3 + 1}
    if(i == "T"){t3 <- t3 + 1}
    if(i == "C"){c3 <- c3 + 1}
    if(i == "G"){g3 <- g3 + 1}
}
```


### Print out each sequence.
```{r}
print(A5Data$Sequence)
```


### Print out the number of each nucleotide as a table for each of the three sequences.
```{r}
# Create the table
Seqs <- c("Sequence 1", "Sequence 2", "Sequence 3")
id <- c("HQ433692.1", "HQ433694.1", "HQ433691.1")
A <- c(a1, a2, a3)
T <- c(t1, t2, t3)
C <- c(c1, c2, c3)
G <- c(g1, g2, g3)
Total <- c(tot1, tot2, tot3)

Table <- data.frame(Sequences = Seqs, IDs = id, A = A, T = T, C = C, G = G, Total = Total)
Table
```


### Include an image of a bacteria from the internet, and a link to the Wikipedia page about Borrelia burgdorferi
![Borrelia burgdorferi medical images from SlideTeam (https://www.slideteam.net/0714-borrelia-burgdorferi-medical-images-for-powerpoint.html). This medical image has been crafted with borrelia burgdorferi. Borrelia burgdorferi is a bacterial species of the spirochete class of the genus Borrelia. It is predominant causative agent of Lyme disease. This image contains structure of this bacteria and focuses on Endoflagella, Axial filament, Cell membrane and Periplasmic space in internal structure.](./BorreliaBurgdorferi.png)

#### [Wikipedia link for Borrelia burgdorferi](https://en.wikipedia.org/wiki/Borrelia_burgdorferi)


### Calculate GC Content (% of nucleotides that are G or C) and create a final table showing GC content for each sequence ID
```{r}
# Calculate the GC content
gc <- (C + G)/Total
GC <- format(round(gc*100, 2))
gc_content <- paste(GC,"%", sep = "")

# Make the table
GCTable <- data.frame(Sequence_ID = id, GC_content = gc_content)
GCTable
```
